---
title: "Quick Analysis"
author: " "
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(tidytext)
library(stopwords)
library(wordcloud)
library(RColorBrewer)
library(plotly)
library(topicmodels)
library(corrplot)
 
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Loading datasets
if (file.exists("text/text_1.txt")){
  text_1 <- read.delim("text/text_1.txt", col.names=c("text"), stringsAsFactors = FALSE)%>% 
    mutate(linenumber = row_number(),
           book = 1)%>%
    mutate(color = "#F8766D")
}else{
  text_1 <- data.frame(matrix(ncol = 3, nrow = 0))
  x <- c("text")
  colnames(text_1) <- x
}

if (file.exists("text/text_2.txt")){
  text_2 <- read.delim("text/text_2.txt", col.names=c("text"), stringsAsFactors = FALSE)%>% 
    mutate(linenumber = row_number(),
           book = 2)%>%
    mutate(color = "#00BFC4")
}else{
  text_2 <- data.frame(matrix(ncol = 3, nrow = 0))
  x <- c("text")
  colnames(text_2) <- x
}

if (file.exists("text/text_3.txt")){
  text_3 <- read.delim("text/text_2.txt", col.names=c("text"), stringsAsFactors = FALSE)%>% 
    mutate(linenumber = row_number(),
           book = 3)%>%
    mutate(color = "#7A5C58")
}else{
  text_3 <- data.frame(matrix(ncol = 3, nrow = 0))
  x <- c("text")
  colnames(text_3) <- x
}

dataset_raw <- text_1 %>%
  rbind(text_2) %>%
  rbind(text_3)

prepare_data <- function(data){
  if (nrow(data) == 0){
    data
  }else{
    data %>% 
      unnest_tokens(word, text) %>% 
      anti_join(stop_words)}}

dataset_1 <- prepare_data(text_1)
dataset_2 <- prepare_data(text_2)
dataset_3 <- prepare_data(text_3)

dataset_unnested <- dataset_1 %>%
  rbind(dataset_2) %>%
  rbind(dataset_3)
```

 

# Text mining

##### Frequency analysis with wordcloud 
This is a wordcloud, a collection, or cluster, of words depicted in different sizes. The biggest and boldest the word appears, the more often it's mentioned within a given text. The documents are divided per color: <span style="color: #F8766D;">text_1</span>, <span style="color: #00BFC4;">text_2</span> and <span style="color: #7A5C58;">text_3</span>.\n

```{r wordcloud_words, echo=FALSE, collapse=TRUE, warning=FALSE}
words_for_cloud <- dataset_unnested %>%
  count(word, book, color, sort = TRUE) 

wordcloud(words = words_for_cloud$word, freq = words_for_cloud$n, min.freq = 60,
          max.words = 200, random.order = FALSE, random.color = FALSE, rot.per = 0.35, 
          colors = (words_for_cloud$color), ordered.colors = TRUE)
```


##### Bigrams analysis 
In this case I consider bigrams. This is a plot which each point corrispondes to a bigram (you can check which of them hovering with mouse). \n

```{r most_used_bigrams, echo=FALSE,  include=FALSE, collapse=TRUE, warning=FALSE}
dataset_counts_dataset <- dataset_raw %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  count(bigram, book, color, sort = TRUE) %>%
  filter(n > 3) %>% #bigrams with at least 4 occurrences, in order to have lighter graphic
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)  %>%
  na.omit() %>%
  unite("bigram", word1, word2, sep = " ") 


p <- dataset_counts_dataset %>%
  ggplot(aes(book, n, color = color,
             text = paste0("Bigram: ", bigram,
                           "\n Occurrences: ", n))) +
  geom_point(position = position_jitter(width = 0.48)) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x = "Text",
        y = "# of bigrams") +
  scale_color_manual(values = c("#00BFC4", "#F8766D", "#7A5C58")) 
```
```{r plot_bigrams, echo=FALSE, collapse=TRUE, warning=FALSE}
font = list(
  size = 15,
  color = "white"
)

label = list(
  bordercolor = "transparent",
  font = font
)
ggplotly(p, tooltip = c("text")) %>%
  config(displayModeBar = FALSE) %>%
  style(hoverlabel = label) %>%
  layout(font = font,
         yaxis = list(fixedrange = TRUE),
         xaxis = list(fixedrange = TRUE))
```



##### Correlation between the dataset, how these dataset are related?
This is a correlation matrix. Below is reported the correlation between the texts. The possible values are in [-1,+1], in particular: \n

+ +1 means high positive correlation 
+ 0 means no correlation 
+ -1 negative correlation 

```{r corrplot, echo=FALSE, warning=FALSE}
frequency <- dataset_unnested %>%
  count(book, word, sort = TRUE) %>%
  group_by(book) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(book, proportion) 

frequency_matrix <- cor(frequency[, c(-1)], use = "pairwise.complete.obs") %>%
  corrplot(method = "number")
```


# Sentiment analysis

##### Sentiment anlysis 
The sentiments are ranked basing on the sum of the words linked to that sentiment. I use colors to highlight <span style="color: #FE6D73;">negative</span> and <span style="color: #ADF7B6;">positive</span> sentiments. 
```{r sentiments_in_the_text_n, echo=FALSE, collapse=TRUE, include=FALSE}
dataset_sentiment <- dataset_unnested %>% 
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  arrange(sentiment) 
dataset_sentiment <- aggregate(n ~ sentiment, dataset_sentiment,  sum)


dataset_sentiment_words <- dataset_unnested %>% 
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice(2:2) %>% #second word is more significant
  select(word, sentiment)


dataset_counts <- dataset_sentiment %>% 
  full_join(dataset_sentiment_words) %>%
  mutate(isPositive = (sentiment == "trust" | sentiment == "surprise" | sentiment == "positive" | sentiment == "joy")) %>%
  filter(sentiment != "positive", sentiment != "negative") %>%
  mutate(sentiment = reorder(sentiment, n)) %>%
  arrange(desc(n))
dataset_counts

p <- dataset_counts %>%
  ggplot(aes(sentiment, n, fill = isPositive,
             text = paste0("Most used word: ", word,
                           "\nOccurences: ", n,
                           "\nSentiment: ", sentiment))) +
  geom_col(show.legend = FALSE) +
  theme_classic() +
  scale_fill_manual(values = c("#FE6D73", "#ADF7B6")) +
  labs(x = "Sentiment\n\n", y = "# of occurences of that words") +
  theme(legend.position = "none",
        text = element_text(family = "Arial"),
        plot.title = element_text(hjust = 0.5)) +
  coord_flip() 
```
```{r sentiments_in_the_text_nplot, echo=FALSE, collapse=TRUE, warning=FALSE}
font = list(
  size = 15,
  color = "white"
)

label = list(
  bordercolor = "transparent",
  font = font
)

ggplotly(p, tooltip = c("text")) %>%
  config(displayModeBar = FALSE) %>%
  style(hoverlabel = label) %>%
  layout(font = font,
         yaxis = list(fixedrange = TRUE),
         xaxis = list(fixedrange = TRUE))
```



# Topic Modeling

##### Comparison of the topics of the texts
LDA algorithm finds the nine highest per-topic-per-word probabilities, called “beta”. This is an unsupervised method thus that each founded topic has not a label. Recall the colors of <span style="color: #F8766D;">text_1</span>, <span style="color: #00BFC4;">text_2</span> and <span style="color: #7A5C58;">text_3</span>. \n

```{r topic_modelling_versus, echo=FALSE,  include=FALSE, collapse=TRUE, warning=FALSE}
word_counts <- dataset_unnested %>%
  count(book, word, sort = TRUE) %>%
  ungroup()

text_n_dtm <- word_counts %>%
  cast_dtm(book, word, n)

colors <- c("#F8766D", "#7A5C58", "#F8766D", "#7A5C58", "#00BFC4", "#F8766D", "#00BFC4", "#00BFC4", "#7A5C58")

text_n_lda <- LDA(text_n_dtm, k = 9, control = list(seed = 1234)) # k = n topics 

text_n_topics_beta <- tidy(text_n_lda, matrix = "beta")
```
```{r topic_modelling_versus_plot, echo=FALSE,   collapse=TRUE, warning=FALSE}
top_terms <- text_n_topics_beta %>%
  mutate(word = term, term = reorder_within(term, beta, topic)) %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  slice(1:6) 

top_terms %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  labs(title = "", x = "Terms\n", y = expression(beta)) + 
  theme(axis.text.y = element_blank(), axis.ticks = element_blank()) +
  scale_x_reordered(sep = "___") +
  scale_fill_manual(values = colors) +
  coord_flip() +
  theme_classic()
```


##### Linking topics with texts
In order to label the topics we use the per-document-per-topic probabilities, called “gamma”. \n

```{r topic_modelling_versus_boxplot, echo=FALSE,   collapse=TRUE, warning=FALSE}
text_n_topics_gamma <- tidy(text_n_lda, matrix = "gamma")

chapters_gamma <- text_n_topics_gamma %>%
  separate(document, c("title"), sep = "_", convert = TRUE)

chapters_gamma %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title) +
  labs(x = "topic", y = expression(gamma)) +
  theme_classic()
```

